%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerstyle{Steven Steiner} \\
	\vspace{2mm}
	{\faEnvelope\ steven.i.steiner@gmail.com} | {\faMapMarker\ Los Angeles, CA} | {\faGithub\ github.com/steets250}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{B.S. in Computer Science}
	{University of California San Diego}
	{La Jolla, CA}
	{Sep 2018 – Jun 2022}
	{\begin{cvitems}
		\item {GPA: 3.75}
		\item {Courses: Object-Oriented Design, Data Structures, Algorithm Theory/Design, Software Engineering}
		\end{cvitems}}
\end{cventries}

\vspace{-5mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
\cventry
	{Front-End Developer}
	{Association for Computing Machinery at UCSD}
	{La Jolla, CA}
	{May 2020 – Present}
	{\begin{cvitems}
		\item {Correcting visual CSS and behavioral Redux bugs in existing React codebase.}
		\item {Developing improved user check-in process used by over 1000 members.}
		\item {Rewriting site functions to improve code cleanliness and readability.}
		\item {Maintaining communication with team using Agile development strategies. }
		\end{cvitems}}
	\cventry
	{Front-End Developer}
	{IntElect}
	{La Jolla, CA}
	{Mar 2020 – Present}
	{\begin{cvitems}
		\item {Developing education recommendation platform using React.}
		\item {Interfacing with Express backend API to power site logic.}
		\item {Assisting with the design of site elements using the Figma design tool.}
		\end{cvitems}}
	\cventry
	{File Clerk}
	{Lurie, Zepeda, et al.}
	{Century City, CA}
	{Jul – Sep 2019, Jun - Sep 2020}
	{\begin{cvitems}
		\item {Processed and indexed legal documents and daily briefings for legal staff.}
		\item {Organized legal files and helped to implement case archival processes.}
		\item {Provided technical support to employees working from home.}
		\end{cvitems}}
\end{cventries}

\vspace{-5mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Projects}
\begin{cventries}
	\cventry
	{Personal Project}
	{Venice High App}
	{}
	{iPhone App Store: \textquotedbl{}Venice High\textquotedbl{}}
	{\begin{cvitems}
		\item {Developed informational mobile app geared towards high school students, parents, and staff.}
		\item {Created user interface in Xcode and app logic using Swift. Utilized CocoaPods libraries.}
		\item {Responded to user feedback and continually adapted the program to meet user requests.}
		\item {Earned a 4.8 star rating and received over 1.5k downloads.}
		\end{cvitems}}
	\cventry
	{UCSD Triton XR Club Project}
	{Endeavor}
	{}
	{github.com/TritonXR/Endeavor}
	{\begin{cvitems}
		\item {Programmed logic for a puzzle game exploring the capabilities of virtual reality.}
		\item {Added game visuals using the Unity engine and programmed game logic in C\#.}
		\item {Assisted teammates in game scripting and interfacing with the Oculus VR library.}
		\end{cvitems}}
	\cventry
	{Hackathon Project}
	{MakeCents}
	{}
	{github.com/jeffrey447/makecents}
	{\begin{cvitems}
		\item {Created React frontend for hackathon project designed to improve donation frequency for users.}
		\item {Interfaced with third-party payment APIs to demonstrate project capabilities.}
		\item {Won the Script Foundation Social team of the year award.}
		\end{cvitems}}
	\cventry
	{Personal Project}
	{Ring Home Automation Plugin}
	{}
	{github.com/steets250/vera-ring}
	{\begin{cvitems}
		\item {Scripted plugin for Vera home automation controllers to interface with Ring security devices.}
		\item {Ported and refactored existing Javascript API to the Lua language.}
		\item {Tested on multiple hardware platforms, diagnosed code bugs, and revised plugin.}
		\end{cvitems}}
\end{cventries}

\vspace{-5mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Programming Languages:  & {\skill{ Javascript, C++, Java, Swift, C, C\#, ARM}} \\
		 \\
		Frameworks/Software:  & {\skill{ Node.js, React, Npm/Yarn, Git/GitHub, Xcode, Unity}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\end{document}